\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-09 paper/main.tex
.

we built protein function and ontology based features based on DL2vec

Ontology derived protein function focused features are highly predictive for dtis

We built a versatile template for various features to test localization on the PPI graph

normal GCNs don't work on PPI graph, as it is highly connected $\rightarrow$ needs stronger more expressive aggregation function $\rightarrow$ GENConv in residual blocks for better numerical stability

molecular features work for all (most?) drugs, top-down features only
for those that have a side-effect profile

\begin{itemize}
	\item \name{} comparison to other approaches on BioSnap prone to bias, as $ BioSnap: drugs 
	\times prots = 5500 \times 3000 $, while only 
	$\approx$ 1000 drugs have Sider Annotation, and 
\end{itemize}

\subsection{Evaluating drug--target interaction predictions}

>>>>

Combining bottom-up and top-down approaches in a single model can
follow different strategies. Interaction networks are used widely to
determine indirect effects of molecular changes \cite{} and predict
drug--target interactions \cite{}. Our work relies on graph neural
networks as a way to combine qualitative information about
interactions with additional features (molecular interaction,
phenotypic and functional features); even if only some of these
features benefit from the information the graph provides, graph neural
networks will allow further extension of our model with additional
features in the future.

% Graph neural networks \cite{} have the ability to
% represent interaction networks

% we built protein function and ontology based features based on DL2vec

% Ontology derived protein function focused features are highly predictive for dtis

% We built a versatile template for various features to test localization on the PPI graph

% normal GCNs don't work on PPI graph, as it is highly connected $\rightarrow$ needs stronger more expressive aggregation function $\rightarrow$ GENConv in residual blocks for better numerical stability

% molecular features work for all (most?) drugs, top-down features only
% for those that have a side-effect profile

% \begin{itemize}
% 	\item \name{} comparison to other approaches on BioSnap prone to bias, as $ BioSnap: drugs 
% 	\times prots = 5500 \times 3000 $, while only 
% 	$\approx$ 1000 drugs have Sider Annotation, and 
% \end{itemize}

\subsection{The challenge of evaluating drug--target interaction
  predictions}
